---
title: "Ruan Code"
author: "Anyue Ruan"
date: "2022-10-13"
output: html_document
---

```{r, loaddata, include=FALSE}
course_engagement <- read.csv("C:/Users/Anyue/OneDrive/Desktop/CLASS/Emory/Semester 3/INFO 550/Engagement report/course_engagement.csv")
course_engagement2 <- read.csv("C:/Users/Anyue/OneDrive/Desktop/CLASS/Emory/Semester 3/INFO 550/Engagement report/course_engagement.csv")
```

#Examine the correlation between length of video and engagement
#  Using regression to plot and analyze the correlation between length of video and engagement

```{r}
library(labelled)
library(gtsummary)
library(lubridate)

course_engagement$length <- (as.numeric(ms(course_engagement$length)))
course_engagement$length[4] <- (as.numeric(hms(course_engagement2$length[4])))
course_engagement$length <- round(x=(course_engagement$length)/60,digits = 2)
```

```{r}
#course <- course_engagement[is.na(course_engagement)] <- 0

# Creating the plot
plot(course_engagement$length ~ course_engagement$unique_viewers, pch = 19, col = "lightblue")

# Regression line
abline(lm(course_engagement$length ~ course_engagement$unique_viewers), col = "red", lwd = 3)
```

```{r}
analyze <- lm(course_engagement$length ~ course_engagement$unique_viewers)
```






#Study time trends of engagement over weeks of class
#  Analyzing the tendency by doing regression as well
```{r}
plot(course_engagement$length ~ course_engagement$views, pch = 19, col = "lightblue")
abline(lm(course_engagement$length ~ course_engagement$views), col = "red", lwd = 3)
```
```{r}
lm(course_engagement$length ~ course_engagement$views)
```






#Study time trends of engagement through each week
#  Analyzing the tendency by doing regression as well
```{r}
plot(course_engagement$length ~ course_engagement$week, pch = 19, col = "lightblue")
abline(lm(course_engagement$length ~ course_engagement$week), col = "red", lwd = 3)
```
```{r}
lm(course_engagement$length ~ course_engagement$week)
```




